---
title: "week1 part b"
author: "Thanh Elsener"
date: "9/21/2020"
output: 
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = TRUE}
set.seed(2020)
LN <- rlnorm(100, meanlog = 1, sdlog = 25)
```

```{css style, echo=FALSE}
p {
  font-size: 20px;
}

h1, h2, h3 {
  text-align: center;
}
```

<section>
<h2>Section 1 </h2>
<p> Below is the histogram of simulated data </p>


```{r, echo = TRUE}
hist(LN, breaks = 20)
mean_normal <- round(mean(LN),3)
sd_normal <- round(sd(LN),3)
```

<p> mean of the observed data is `r toString(mean_normal)` and the standard deviation is `r toString(sd_normal)`</p>

<p> Histogram shows a very right-skewed distribution and all data points have positive values. So in practice, log transformation will be performed on data </p>
</section>

<section>
<h2>Section 2</h2>
<p> Below is the histogram of the log-transfomation of the simulated data</p>


```{r}
hist(log(LN), breaks = 20)
mean_log <- round(mean(log(LN)),3)
sd_log <- round(sd(log(LN)),3)
```

<p> mean of the log-transformed data is `r toString(mean_log)` and the standard deviation is `r toString(sd_log)`</p>

</section>



